\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-01 paper.tex
rewrite some of MCMC

\subsection{MCMC}
\label{subsec:mcmc}
Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
A set of samples are generated to approximate the desired distribution $ \pi (x) $.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.
The concept origins from Hamiltonian dynamics, which models the movement of an object, the position $ x $ and the momentum $ q $ over time $ t $.
Define a system energy $ H $ of an object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
By the Hamiltonian equation, the movement of the object can be predicted by
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
This provides an approach of the gradient descent by following the decrease of an associated potential energy.
Thus, HMC simulates the Hamiltonian dynamics that moves samples towards a target distribution while avoiding random walks.

@@

\section{Motivating example---Minimal-Time Double Integrator}
We start by considering a simple yet important motion-planning problem---the double integrator.
We are given a one-dimensional point robot  with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.

>>>>

\subsection{MCMC}
\label{subsec:mcmc}

Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
A set of samples are generated to approximate the desired distribution $ \pi (x) $.
A approximated desired distribution $ \hat{\pi} (x) $ can be used in any problem that states are modeled random variable, e.g. motion tracking~\cite{KBD04}, data regression~\cite{TL11} and state estimation~\cite{ASC13}.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important area, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.
The concept origins from Hamiltonian dynamics, which models the movement of an object, the position $ x $ and the momentum $ q $ over time $ t $.
Define a system energy $ H $ of an object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
By the Hamiltonian equation, the movement of the object can be predicted by
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
This provides an approach of the gradient descent by following the decrease of an associated potential energy.
Thus, HMC simulates the Hamiltonian dynamics that moves samples towards a target distribution while avoiding random walks.

@@

\section{Motivating example---Minimal-Time Double Integrator}

We start by considering a simple yet important dynamical system---the double integrator. 
We are given a one-dimensional point robot with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
